The Astropy Project

### 2017-12-14 main.tex
added footnote and author input

\author{Astropy Collaboration}

>>>>

\author{Astropy Project}
\footnote{The author list has three parts: the 13 authors that were primary authors of  sections of the paper in order of contribution, the four members of the \astropy Project coordination committee, and contributions to the \astropy Project in alphabetical order.  The position in the author list does not correspond to contributions to the \astropy Project as a whole.  A more complete list of contributors to the core package can be found in the \href{https://github.com/astropy/astropy/graphs/contributors}{package repository}, and at the \href{http://www.astropy.org/team.html}{\astropy team webpage}.}

\input{author.tex}
